Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-06-04 paper.tex
Add doppler shift test

\subsection{Doppler Shift}
\label{ssec:test_doppler}
Homogeneous matter moving with v in +z direction. Stationary observer.
\todo{add plot of $\varepsilon(\mu)$}

@@

>>>>

\subsection{Doppler Shift}
\label{ssec:test_doppler}
Homogeneous matter moving with v in +z direction. Stationary observer.
Plot in Fig.~\ref{fig:avg_eps_doppler}.
\todo{describe test}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-moving_fluid-avg_eps_vs_cosA}
  \caption{Average energy $\langle\varepsilon\rangle=J/G$
    of neutrino fields for fluid moving in the $+z$ direction,
    with $A$ the angle between the neutrino momentum and the $+z$ direction.
    Test described in Sec.~\ref{ssec:test_doppler}}
  \label{fig:avg_eps_doppler}
\end{figure}
